tag_loss

### 2022-09-22 smelt_2019_winterspring/Diet.Rmd
updates to diet analysis to explore random effect of cage

# load packages
```{r}
library(tidyverse)
library(lubridate)
library(emmeans)
library(multcompView)
```

@@

#average for IR & fullness
mean.IR<- total %>% 
  group_by(Location, Mesh, Tag) %>% 
  summarize("mean.IR"= mean(IR), "mean.full"=mean(Fullness))

#split into RV and DWSC
split<- split(mean.IR, mean.IR$Location)
write_excel_csv(split[["RVR"]], "smelt_2019_winterspring/data_raw/diet.RVR.csv")
write_excel_csv(split[["DWSC"]], "smelt_2019_winterspring/data_raw/diet.DWSC.csv")
RVR<- read_csv("smelt_2019_winterspring/data_raw/diet.RVR.csv")
DWSC<- read_csv("smelt_2019_winterspring/data_raw/diet.DWSC.csv")

@@

#log transform
RVR[,6] <- log(RVR[c(4)] +1)
shapiro.test(RVR$mean.IR.1) #insiginificant
plotNormalHistogram(RVR$mean.IR.1)

DWSC$mean.IR.1 <- log(DWSC[c(4)] +1)
shapiro.test(DWSC$mean.IR.1) #insiginificant
plotNormalHistogram(DWSC$mean.IR.1)

#RVR anova 
RVR.IR.mod <- lm(mean.IR.1 ~ Mesh, data=RVR)
anova(RVR.IR.mod) #significant

@@

CLD(marginal,
    alpha   = 0.05, 
    Letters = letters,     
    adjust  = "tukey")

#DWSC anova 
DW.IR.mod <- lm(mean.IR.1 ~ Mesh, data=DWSC)
anova(DW.IR.mod) #insignificant

@@

CLD(marginal,
    alpha   = 0.05, 
    Letters = letters,     
    adjust  = "tukey")
```

# percent of each taxa for new Table 7 created on 3/7/2022
```{r}
diet_type$Count[which(diet_type$Count == "1 maybe 2")] <- 2

taxa.perct$percent <- (taxa.perct$count.sum/taxa.perct$Total)*100

split<- split(taxa.perct, taxa.perct$Location)
write_excel_csv(split[["RVR"]], "C:/Users/nkwan/Desktop/diet winter '19/perc.RVR.csv")
write_excel_csv(split[["DWSC"]], "C:/Users/nkwan/Desktop/diet winter '19/perc.DWSC.csv")
RVR.p<- read_csv("perc.RVR.csv")
DWSC.p<- read_csv("perc.DWSC.csv")

taxa.perct2 <- merge(RVR.p, DWSC.p, by="Prey.Taxa", all = TRUE)

taxa.perct2[is.na(taxa.perct2)] = 0

taxa.perct3 <- taxa.perct2[c(1,3,4,6,8,9,11)]

write_excel_csv(taxa.perct3, "C:/Users/nkwan/Desktop/diet winter '19/tableresults.csv")
```

@@

# plot count proportion in 100% stacked bar - final figure
```{r}
#remove empty
full.count.e<-full.count[full.count$Taxa != "empty",]

cbPalette <- c("#F0E442", "#E69F00", "#009E73", "#56B4E9", "#CC79A7", "#D55E00", "#0072B2", "#8C8C8C")
legend_title <- "Taxa"

ggplot(data=full.count.e, aes(x=Mesh, y =count.sum)) +
    geom_bar(aes(fill=factor(Taxa, levels=c("Amphipoda", "Calanoida", "Cladocera", "Cyclopoida", "Diptera", "Harpacticoda", "Ostracoda", "Other"))),  position="fill", stat="identity") +
  facet_grid(~Location)+
  theme_bw() + 
  scale_fill_manual(legend_title, values=cbPalette)+
  theme(legend.position="right", axis.title.x = element_blank())+
  labs(y = "Proportion of Prey Consumed") +  
  theme(panel.grid.major = element_line(colour = "gray93",size=0.01), panel.grid.minor = element_blank()) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(axis.title = element_text(size = 23), 
    axis.text = element_text(size = 20), 
    axis.text.x = element_text(size = 20), 
    axis.text.y = element_text(size = 20), 
    legend.text = element_text(size = 20), 
    legend.title = element_text(size = 20))+
  theme(strip.text.x = element_text(size = 20))
```

@@

#bar plot
ggplot(data=diet.prop.mean.e, aes(x=Mesh, y =prop.mean)) +
    geom_bar(aes(fill=factor(Taxa, levels=c("Amphipoda", "Calanoida", "Cladocera", "Cyclopoida", "Diptera", "Harpacticoda", "Ostracoda", "Other"))), position="dodge", stat="identity") +
  facet_grid(~Location)+
  theme_bw() + 
  scale_fill_manual(legend_title, values=cbPalette)+
  theme(legend.position="right", axis.title.x = element_blank())+
  labs(y = "Average Proportion of Diet") +  
  theme(panel.grid.major = element_line(colour = "gray93",size=0.01), panel.grid.minor = element_blank()) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(axis.title = element_text(size = 23), 
    axis.text = element_text(size = 20), 
    axis.text.x = element_text(size = 20), 
    axis.text.y = element_text(size = 20), 
    legend.text = element_text(size = 20), 
    legend.title = element_text(size = 25))+
  theme(strip.text.x = element_text(size = 20))

#stack bar plot
windowsFonts(Times = windowsFont("Times New Roman"))

d<-ggplot(data=diet.prop.mean.e, aes(x=Mesh, y =prop.mean)) +
    geom_bar(aes(fill=factor(Taxa, levels=c("Amphipoda", "Calanoida", "Cladocera", "Cyclopoida", "Diptera", "Harpacticoda", "Ostracoda", "Other"))), position="fill", stat="identity") +
  facet_grid(~Location)+
  theme_bw() + 
  scale_fill_manual(legend_title, values=cbPalette)+
  scale_y_continuous(labels=percent)+
  theme(legend.position="right", axis.title.x = element_blank())+
  labs(y = "Mean Contribution to Diet") +  
  theme(panel.grid.major = element_line(colour = "gray93",size=0.01), panel.grid.minor = element_blank()) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(axis.title = element_text(size = 17), 
    axis.text = element_text(size = 16), 
    legend.text = element_text(size = 16), 
    legend.title = element_text(size = 17),
    strip.text.x = element_text(size = 17),
    text=element_text(family = "Times"))
print(d)

tiff(filename="Fig6.tiff", 
    units="in", 
    width=7.25, #or 3.5 for single column
    height=4.00, #height you can adjust according to your plot
    res=600, compression="lzw")
print(d)
dev.off()

write_excel_csv(diet.prop.mean.e, "C:/Users/Nicole Aha/Desktop/Analysis/Analysis/Data/diet.prop.mean.csv")
```

>>>>

# load packages
```{r}
library(tidyverse)
library(lubridate)
library(emmeans)
library(multcomp)
library(rcompanion)
library(lme4)
library(Rcpp)
```

@@

#average for IR & fullness
mean.IR<- total %>% 
  group_by(Location, Mesh, Tag, Cage.ID) %>% 
  summarize("mean.IR"= mean(IR), "mean.full"=mean(Fullness))

#split into RV and DWSC
split<- split(mean.IR, mean.IR$Location)
#write_excel_csv(split[["RVR"]], "smelt_2019_winterspring/data_raw/diet.RVR.csv")
#write_excel_csv(split[["DWSC"]], "smelt_2019_winterspring/data_raw/diet.DWSC.csv")
RVR<- read_csv("smelt_2019_winterspring/data_raw/diet.RVR.csv")
DWSC<- read_csv("smelt_2019_winterspring/data_raw/diet.DWSC.csv")

@@

#log transform
RVR$mean.IR.log <- log(RVR$mean.IR +1)
shapiro.test(RVR$mean.IR.log) #insignificant
plotNormalHistogram(RVR$mean.IR.log)

DWSC$mean.IR.log <- log(DWSC$mean.IR +1)
shapiro.test(DWSC$mean.IR.log) #insignificant
plotNormalHistogram(DWSC$mean.IR.log)

#RVR anova 
RVR.IR.mod <- lm(mean.IR.log ~ Mesh, data=RVR)
anova(RVR.IR.mod) #significant

@@

cld(marginal,
    alpha   = 0.05, 
    Letters = letters,     
    adjust  = "tukey")

#Should Cage.ID be included as a random effect? Looked over with Rosie and lmer model gives singularity issue, seperate models with Cage.ID don't show significance - okay to leave out
  #ggplot(RVR,aes(x=Mesh,y=mean.IR.log,col=Cage.ID)) + geom_jitter() + geom_boxplot(alpha=0.2)
  #RVR.IR.mod2 <- lmer(mean.IR.log ~ Mesh + (1|Cage.ID), data=RVR)
  #summary(mod)
  #ranef(RVR.IR.mod2) #saying no variance by cage
  #RVR.IR.mod3 <- lm(mean.IR.log ~ Cage.ID, data=RVR)
  #RVR.IR.mod4 <- lm(mean.IR.log ~ Mesh + Cage.ID, data=RVR)

#DWSC anova 
DW.IR.mod <- lm(mean.IR.log ~ Mesh, data=DWSC)
anova(DW.IR.mod) #insignificant

DW.IR.mod2 <- lmer(mean.IR.log ~ Mesh + (1|Cage.ID), data=DWSC)

ranef(DW.IR.mod2) #close to 0 but some variance

ggplot(DWSC,aes(x=Mesh,y=mean.IR.log,col=Cage.ID)) + geom_jitter() + geom_boxplot(alpha=0.2)

anova(DW.IR.mod2)

@@

cld(marginal,
    alpha   = 0.05, 
    Letters = letters,     
    adjust  = "tukey")
```

@@

@@

#change labels
diet.prop.mean.e$Mesh[diet.prop.mean.e$Mesh == "large"] <- "B"
diet.prop.mean.e$Mesh[diet.prop.mean.e$Mesh == "small"] <- "A"
diet.prop.mean.e$Mesh[diet.prop.mean.e$Mesh == "wrap"] <- "C"

#plot
windowsFonts(Times = windowsFont("Times New Roman"))

d<-ggplot(data=diet.prop.mean.e, aes(x=Mesh, y =prop.mean)) +
    geom_bar(aes(fill=factor(Taxa, levels=c("Amphipoda", "Calanoida", "Cladocera", "Cyclopoida", "Diptera", "Harpacticoda", "Ostracoda", "Other"))), position="fill", stat="identity") +
  facet_grid(~Location)+
  theme_bw() + 
  scale_fill_manual(legend_title, values=cbPalette)+
  scale_y_continuous(labels = scales::percent)+
  theme(legend.position="right", axis.title.x = element_blank())+
  labs(y = "Mean Contribution to Diet") +  
  theme(panel.grid.major = element_line(colour = "gray93",size=0.01), panel.grid.minor = element_blank()) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(axis.title = element_text(size = 17), 
    axis.text = element_text(size = 16), 
    legend.text = element_text(size = 16), 
    legend.title = element_text(size = 17),
    strip.text.x = element_text(size = 17),
    text=element_text(family = "Times"))
d

tiff(filename="smelt_2019_winterspring/figures/dietfig.tiff", 
    units="in", 
    width=7.25, #or 3.5 for single column
    height=4.00, #height you can adjust according to your plot
    res=600, compression="lzw")
print(d)
dev.off()
```

# percent of each taxa for potential supplemental table
```{r}
diet_type$Count[which(diet_type$Count == "1 maybe 2")] <- 2

taxa.perct$percent <- (taxa.perct$count.sum/taxa.perct$Total)*100
```
